---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nytapi

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/clessn/wikirest/branch/main/graph/badge.svg)](https://app.codecov.io/gh/clessn/wikirest?branch=main)
[![R-CMD-check](https://github.com/clessn/nytapi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/clessn/nytapi/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of nytapi is to get data from the New York Times API.

## Installation

You can install the development version of nytapi from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clessn/nytapi")
```

## Usage

1. Get API key from [developer.nytimes.com/](https://developer.nytimes.com/)
2. Save the access token to R environ using `usethis::edit_r_environ()`

```{r eval = FALSE}
# .Renviron
NYT_KEY = "keystring"
```

3. Use key in functions

```{r eval = FALSE}
search_articles(query = "Wikipedia", key = Sys.getenv("NYT_KEY"))
```

## Examples

### Search articles

```{r}
library("nytapi")

json <- search_articles(query = "Wikipedia", key = Sys.getenv("NYT_KEY"))

# Preview of first article
article <- json[["response"]][["docs"]][[1]]

article[["abstract"]]
article[["web_url"]]
article[["snippet"]]
```

### Get most viewed articles

```{r}
json <- get_most_viewed(key = Sys.getenv("NYT_KEY"))

# Preview of first article
article <- json[["results"]][[1]]

article[["title"]]
article[["byline"]]
article[["published_date"]]
```

## Notes

For API documentation, terms of service and licensing information, see [developer.nytimes.com](https://developer.nytimes.com/).

nytapi is not afiliated with The New York Times.
